\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2014-12-31 Report/project_report.tex
SWF Math
Goodbye mbf, hello Vec!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sliding Window Filter (SWF)} \label{sec:SWF}
In contrast to EKF-SLAM, the aim of the Sliding Window Filter (SWF) is not to construct a globally consistent map, but rather to estimate a vehicle's motion by optimizing a sliding window of vehicle poses and feature positions.
The optimization problem in the SWF is typically solved as a non-linear least squares problem using Gauss-Newton (GN) optimization over a sliding window of $K$ poses observing $M$ features: 
\begin{equation}
\Vec{x} := \bbm \Vec x_0^T & \hdots & \Vec x_K^T & \Vec f_1^T & \hdots & \Vec f_M^T\ebm ^T.
\end{equation}
The optimization applies an update, $ \delta \Vec{x}^*$, by solving the linear system:
\begin{equation}
(\Vec H^T \Vec T ^{-1} \Vec H ) \delta \Vec{x}^*  = - \Vec{H}^T\Vec{T}^{-1}\Vec{e}(\bar{\Vec{x}})
\end{equation}
The matrix $\Vec{H}$ is given by (showing non-zero blocks only)
\begin{equation}
\mathbf{H} = \left[\begin{array}{cccccc}
 -\Vec H_{\Vec x, 1} & \Vec 1 & & &   \\ 
 & -\Vec G_{\Vec x, 1} &  &   -\Vec G_{\Vec f, 1} \\ \hline
 & \ddots & \ddots & \vdots  \\  \hline
 & -\Vec H_{\Vec x, K} & \Vec 1 & \\ 
 & & -\Vec G_{\Vec x, K} &  -\Vec G_{\Vec f, K}   \\  
\end{array}\right], 
\end{equation}
where
\begin{align}
\Vec G_{\Vec x, k} &= \bbm \Vec G_{\Vec x, k}^1 & \hdots & \Vec G_{\Vec x, k}^M \ebm ^T
\\[0.5em]
\Vec G_{\Vec{x}, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}}
    \bbm -\Vec C_{CG} \Vec C_{IG,k} \\[0.5em] \Vec C_{CG} (\Vec C_{IG,k} (\boldsymbol{\rho}_i^{f_j G} - \Vec r_G^{IG,k} ) )^\times  \ebm ^T
\\[0.5em]
\Vec G_{\Vec f, k} &= \underbrace{\bbm \Vec G_{\Vec f, k}^1 & & \\ & & \Vec G_{\Vec f, k}^2 & \\ & & \vdots &  \\ & & & \Vec G_{\Vec f, k}^M \ebm}_{\text{$j$th block column position given by feature ID $j\in[1,M]$}} \\[0.5em]
\Vec G_{\Vec f, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}} \Vec C_{CI} \Vec C_{IG,k}
\end{align}
with
\begin{equation}
\bar{\Vec p}_{C_k}^{f_j C_k} := \bbm x \\ y \\ z \ebm = \Vec C_{CI} \left( \Vec C_{IG,k} (\boldsymbol{\rho}_G^{f_j G} - \Vec r_G^{IG,k} )   - \boldsymbol \rho_I^{CI} \right),
\end{equation}

@@

The weight matrix $\mbf T$ is given by:
\begin{equation}
\Vec{T} := \text{diag} \left\{ \Vec{T}_1,\hdots,\Vec{T}_K \right\}
\end{equation}
where
\begin{equation}
\mbf{T}_k := \bbm \mbf H_{\mbf w, k} \mbf Q_k \mbf H_{\mbf w, k}^T & \mbf 0 \\
\mbf 0 & \mbf G_{\mbf n, k} \mbf R_k \mbf G_{\mbf n, k}^T \ebm,
\end{equation}
and $\mbf R_k$, $\mbf Q_k$ are observation and motion model noise covariances, and $\mbf G_{\mbf n, k}$, $\mbf H_{\mbf w, k}$ are the observation and motion model Jacobians with respect to the noise.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sliding Window Filter (SWF)} \label{sec:SWF}
In contrast to EKF-SLAM, the aim of the Sliding Window Filter (SWF) is not to construct a globally consistent map, but rather to estimate a vehicle's motion by optimizing a sliding window of vehicle poses and feature positions.
The optimization problem in the SWF is typically solved as a non-linear least squares problem using Gauss-Newton (GN) optimization over a sliding window of $K$ poses observing $M$ features: 
\begin{equation}
\Vec{x} := \bbm \Vec x_0^T & \hdots & \Vec x_K^T & {\Vec {p}_G^{f_1G}}^T & \hdots & {\Vec {p}_G^{f_MG}}^T \ebm ^T.
\end{equation}
The optimization applies an update, $ \delta \Vec{x}^*$, by solving the linear system:
\begin{equation}
(\Vec H^T \Vec T ^{-1} \Vec H ) \delta \Vec{x}^*  = - \Vec{H}^T\Vec{T}^{-1}\Vec{e}(\bar{\Vec{x}})
\end{equation}
The matrix $\Vec{H}$ is given by (showing non-zero blocks only)
\begin{equation}
\mathbf{H} = \left[\begin{array}{cccccc}
 -\Vec H_{\Vec x, 1} & \Vec 1 & & &   \\ 
 & -\Vec G_{\Vec x, 1} &  &   -\Vec G_{\Vec f, 1} \\ \hline
 & \ddots & \ddots & \vdots  \\  \hline
 & -\Vec H_{\Vec x, K} & \Vec 1 & \\ 
 & & -\Vec G_{\Vec x, K} &  -\Vec G_{\Vec f, K}   \\  
\end{array}\right], 
\end{equation}
where
\begin{align}
\Vec G_{\Vec x, k} &= \bbm \Vec G_{\Vec x, k}^1 & \hdots & \Vec G_{\Vec x, k}^M \ebm ^T
\\[0.5em]
\Vec G_{\Vec{x}, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}}
    \bbm -\Vec C_{CG} \Vec C_{IG,k} \\[0.5em] \Vec C_{CG} (\Vec C_{IG,k} (\Vec{p}_G^{f_j G} - \Vec p_G^{IG,k} ) )^\times  \ebm ^T
\\[0.5em]
\Vec G_{\Vec f, k} &= \underbrace{\bbm \Vec G_{\Vec f, k}^1 & & \\ & & \Vec G_{\Vec f, k}^2 & \\ & & \vdots &  \\ & & & \Vec G_{\Vec f, k}^M \ebm}_{\text{$j$th block column position given by feature ID $j\in[1,M]$}} \\[0.5em]
\Vec G_{\Vec f, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}} \Vec C_{CI} \Vec C_{IG,k}
\end{align}
with
\begin{equation}
\bar{\Vec p}_{C_k}^{f_j C_k} := \bbm x \\ y \\ z \ebm = \Vec C_{CI} \left( \Vec C_{IG,k} (\Vec{p}_G^{f_j G} - \Vec{p}_G^{IG,k} )   - \Vec p_I^{CI} \right),
\end{equation}

@@

The weight matrix $\mbf T$ is given by:
\begin{equation}
\Vec{T} := \text{diag} \left\{ \Vec{T}_1,\hdots,\Vec{T}_K \right\}
\end{equation}
where
\begin{equation}
\Vec{T}_k := \bbm \Vec H_{\mbf w, k} \Vec Q_k \Vec H_{\Vec w, k}^T & \Vec 0 \\
\Vec 0 & \Vec G_{\Vec n, k} \Vec R_k \Vec G_{\Vec n, k}^T \ebm,
\end{equation}
and $\mbf R_k$, $\mbf Q_k$ are observation and motion model noise covariances, and $\Vec G_{\Vec n, k}$, $\Vec H_{\Vec w, k}$ are the observation and motion model Jacobians with respect to the noise.
